---
title: "Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

[TEXT IN SQUARE BRACKETS IS HERE FOR GUIDANCE. PLEASE DELETE TEXT IN SQUARE BRACKETS BEFORE KNITTING THE FINAL REPORT]

# Report Details

[PILOT/COPILOT ENTER RELEVANT REPORT DETAILS HERE]

```{r}
articleID <- 6-1-2015 # insert the article ID code here e.g., "10-3-2015"
reportType <- "pilot" # specify whether this is the 'pilot' report or 'copilot' report
pilotNames <- "Kayla Good" # insert the pilot's name here e.g., "Tom Hardwicke".
copilotNames <- "Ashish Mehta" # # insert the co-pilot's name here e.g., "Michael Frank".
pilotTTC <- NA # insert the pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
copilotTTC <- NA # insert the co-pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
pilotStartDate <- as.Date("11/2/19", format = "%m/%d/%y") # insert the piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
copilotStartDate <- NA # insert the co-piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
completionDate <- NA # insert the date of final report completion in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
```

------

#### Methods summary: 

[PILOT/COPILOT write a brief summary of the methods underlying the target outcomes written in your own words]

------

#### Target outcomes: 

For this article you should focus on the findings reported in section "Effects of crowding on perception and action" for Experiment 1.

Specifically, you should attempt to reproduce all descriptive and inferential analyses reported in the text below and associated tables/figures:

> Effects of crowding on perception and action

> Experiment 1 was designed to explore the effects of crowding on perception and action, with a particular focus on whether participants could scale their grip aperture to the size of the target even when they could not consciously identify the size of the target. We carried out a four-way repeated measures ANOVA on the manual estimates and PGAs with task (estimation vs. grasping), crowding condition (uncrowded vs. crowded), viewing condition (closed- vs. open-loop), and target size (3.0 vs. 3.75 cm) as main factors. The significant interaction between task and crowding condition, F(1, 9) = 6.818, p = .028, suggested that crowding had different effects on performance of the grasping and manual estimation tasks. Not surprisingly, when the target was presented in isolation, participants were able to manually estimate the sizes of the two targets—and this was true for both closed-loop trials, t(9) = 7.23, p < .001, and open-loop trials, t(9) = 9.19, p < .001. Similarly, participants showed excellent grip scaling for targets presented in isolation on both closed-loop trials, t(9) = 4.29, p = .002, and openloop trials, t(9) = 4.79, p = .001 (Fig. 3). Things were quite different, however, when the target disks were surrounded by flankers. In this condition, participants could no longer discriminate between the two disk sizes using a manual estimate closed-loop trials: t(9) = 1.02, p = .334; open-loop trials: t(9) = 1.78, p = .108?presumably because the size of the target was perceptually invisible. (Note that we use the term invisible to refer to the fact that participants could not identify the size of the target, even though they were aware of its presence and position.) In contrast, when participants were asked to grasp the same targets, their PGAs were still scaled to target size?closed-loop trials: t(9) = 4.21, p = .002; open-loop trials: t(9) = 3.392, p = .008 (Fig. 3).


------

[PILOT/COPILOT DO NOT CHANGE THE CODE IN THE CHUNK BELOW]  

```{r global_options, include=FALSE}
# sets up some formatting options for the R Markdown document
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages and prepare report object

[PILOT/COPILOT Some useful packages are being loaded below. You can add any additional ones you might need too.]

```{r}
# load packages
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(ReproReports) # custom reporting functions
```

[PILOT/COPILOT DO NOT MAKE CHANGES TO THE CODE CHUNK BELOW]

```{r}
# Prepare report object. This will be updated automatically by the reproCheck function each time values are compared
reportObject <- data.frame(dummyRow = TRUE, reportedValue = NA, obtainedValue = NA, valueType = NA, percentageError = NA, comparisonOutcome = NA, eyeballCheck = NA)
```

# Step 2: Load data

```{r}
raw_data <- read_xlsx("GroupA_6-1-2015/data/data_Exp1.xlsx", sheet = "summary")
```

# Step 3: Tidy data

```{r}
  
clean_data_wide_withmeans <- raw_data %>%
  filter(grepl('sub', ...1) | grepl('mean', ...1)) %>% # removes unnecessary row with condition labels
  filter(!(...1 == "sub")) %>% # removes unnecessary row with condition labels
  rename("SubID" = "...1", 
         "closedloop_grasp_uncrowded_3cm" = "closed-loop grasping",
         "closedloop_grasp_uncrowded_3.75cm" = "...3", 
         "closedloop_grasp_crowded_3cm" = "...4", 
         "closedloop_grasp_crowded_3.75cm" = "...5", 
         "openloop_grasp_uncrowded_3cm" = "open-loop_grasping", 
         "openloop_grasp_uncrowded_3.75cm" = "...8", 
         "openloop_grasp_crowded_3cm" = "...9", 
         "openloop_grasp_crowded_3.75cm" = "...10", 
         "closedloop_estimate_uncrowded_3cm" = "closed-loop estimation",
         "closedloop_estimate_uncrowded_3.75cm" = "...13", 
         "closedloop_estimate_crowded_3cm" = "...14", 
         "closedloop_estimate_crowded_3.75cm" = "...15", 
         "openloop_estimate_uncrowded_3cm" = "open-loop estimation",
         "openloop_estimate_uncrowded_3.75cm" = "...18",
         "openloop_estimate_crowded_3cm" = "...19",
         "openloop_estimate_crowded_3.75cm" = "...20") %>% # Renaming the columns to reflect each subject's score by crowding condition, viewing condition, task, and target size  
   select(-c(...6, ...11, ...16)) # removes columns used for spacing in original Excel file

# Please note that, in the original data file, the target sizes for open-loop estimation were listed as "un5", "un8", "crd5", and "crd8". The paper indicated that the same target sizes (3cm and 3.75cm) were across conditions. "Un" and "crd" clearly correspond to the "uncrowded" and "crowded" conditions, but it was assumed that "5" and "8" correspond to "3cm" and "3.75cm," respectively.
               
i <- c(2:17)
clean_data_wide_withmeans[,i] <- apply(clean_data_wide_withmeans[,i], 2, as.numeric) # converting appropriate columns to numeric data type

```

```{r}
clean_data_long_withmeans <- clean_data_wide_withmeans %>% 
  pivot_longer(-SubID, 
               names_to = "condition", 
               values_to = "score") %>% 
  separate(condition, into=c("viewing_condition", "task", "crowding_condition", "target_size"),
               sep="_") %>% # pivoting data into 'tidy' or 'long' format, with columns to indicate levels of each condition
             select(viewing_condition, task, crowding_condition, target_size, everything())
```

```{r}
clean_data_long_withoutmeans <- clean_data_long_withmeans %>% 
  filter(SubID != "mean") # removing means from data frame
```


# Step 4: Run analysis

## Pre-processing

```{r}
means_from_original_data_long <- clean_data_long_withmeans %>% 
  filter(SubID == "mean") # extracting means reported in original data file

clean_data_wide_withoutmeans <- clean_data_wide_withmeans %>% 
  slice(-11)
```

## Descriptive statistics

```{r}
calculated_means <- clean_data_long_withoutmeans %>% 
  group_by(viewing_condition, task, crowding_condition, target_size) %>% 
  summarise(mean = mean(score),
            sd = sd(score)) %>% 
  ungroup()
```

```{r}
manual_estimation_means <- calculated_means %>% 
  filter(task == "estimate")
```

```{r}
grasping_means <- calculated_means %>% 
  filter(task == "grasp")
```

## Inferential statistics

```{r}
test.aov <- aov((score ~ viewing_condition * task * crowding_condition * target_size + Error(SubID / (viewing_condition * task * crowding_condition * target_size))), data = clean_data_long_withoutmeans)
summary(test.aov) 
```

```{r}
t.test(clean_data_wide_withoutmeans$closedloop_estimate_uncrowded_3.75cm,clean_data_wide_withoutmeans$closedloop_estimate_uncrowded_3cm, paired = TRUE) # t-test comparing manual estimates in the closed-loop condition for different target sizes

t_test_closedloop_estimate_uncrowded_data <- clean_data_long_withoutmeans %>% 
  filter(viewing_condition == "closedloop" & 
           task == "estimate" & 
           crowding_condition == "uncrowded") 

t_test_closedloop_estimate_uncrowded <- t_test_closedloop_estimate_uncrowded_data %>% 
  do(tidy(t.test(score~target_size, data = t_test_closedloop_estimate_uncrowded_data,
                                                       paired=TRUE)))

print(t_test_closedloop_estimate_uncrowded)
```

```{r}
t.test(clean_data_wide_withoutmeans$openloop_estimate_uncrowded_3.75cm,clean_data_wide_withoutmeans$openloop_estimate_uncrowded_3cm, paired = TRUE) # t-test comparing manual estimates in the open-loop condition for different target sizes

t_test_openloop_estimate_uncrowded_data <- clean_data_long_withoutmeans %>% 
  filter(viewing_condition == "openloop" & 
           task == "estimate" & 
           crowding_condition == "uncrowded") 

t_test_openloop_estimate_uncrowded <- t_test_openloop_estimate_uncrowded_data %>% 
  do(tidy(t.test(score~target_size, data = t_test_openloop_estimate_uncrowded_data,
                                                       paired=TRUE)))

print(t_test_openloop_estimate_uncrowded)
```

```{r}
t.test(clean_data_wide_withoutmeans$closedloop_grasp_uncrowded_3.75cm,clean_data_wide_withoutmeans$closedloop_grasp_uncrowded_3cm, paired = TRUE) # t-test comparing manual estimates in the open-loop condition for different target sizes

t_test_closedloop_grasp_uncrowded_data <- clean_data_long_withoutmeans %>% 
  filter(viewing_condition == "closedloop" & 
           task == "grasp" & 
           crowding_condition == "uncrowded") 

t_test_closedloop_grasp_uncrowded <- t_test_closedloop_grasp_uncrowded_data %>% 
  do(tidy(t.test(score~target_size, data = t_test_closedloop_grasp_uncrowded_data,
                                                       paired=TRUE)))

print(t_test_closedloop_grasp_uncrowded)
```

```{r}
t.test(clean_data_wide_withoutmeans$openloop_grasp_uncrowded_3.75cm,clean_data_wide_withoutmeans$openloop_grasp_uncrowded_3cm, paired = TRUE) # t-test comparing manual estimates in the open-loop condition for different target sizes
```

```{r}
t.test(clean_data_wide_withoutmeans$closedloop_estimate_crowded_3.75cm,clean_data_wide_withoutmeans$closedloop_estimate_crowded_3cm, paired = TRUE) # t-test comparing manual estimates in the open-loop condition for different target sizes
```

```{r}
t.test(clean_data_wide_withoutmeans$closedloop_grasp_uncrowded_3.75cm,clean_data_wide_withoutmeans$closedloop_grasp_uncrowded_3cm, paired = TRUE) # t-test comparing manual estimates in the open-loop condition for different target sizes
```

# Step 5: Conclusion

[Please include a text summary describing your findings. If this reproducibility check was a failure, you should note any suggestions as to what you think the likely cause(s) might be.]


[PILOT/COPILOT DOD NOT EDIT THE CODE CHUNK BELOW]

```{r}
reportObject <- reportObject %>%
  filter(dummyRow == FALSE) %>% # remove the dummy row
  select(-dummyRow) %>% # remove dummy row designation
  mutate(articleID = articleID) %>% # add variables to report 
  select(articleID, everything()) # make articleID first column

# decide on final outcome
if(any(reportObject$comparisonOutcome %in% c("MAJOR_ERROR", "DECISION_ERROR"))){
  finalOutcome <- "Failure"
}else{
  finalOutcome <- "Success"
}

# collate report extra details
reportExtras <- data.frame(articleID, pilotNames, copilotNames, pilotTTC, copilotTTC, pilotStartDate, copilotStartDate, completionDate, finalOutcome)

# save report objects
if(reportType == "pilot"){
  write_csv(reportObject, "pilotReportDetailed.csv")
  write_csv(reportExtras, "pilotReportExtras.csv")
}

if(reportType == "copilot"){
  write_csv(reportObject, "copilotReportDetailed.csv")
  write_csv(reportExtras, "copilotReportExtras.csv")
}
```

# Session information

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
